---
title: "linear_models"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
library(viridis)

knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  fig.width = 8,
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(
    borough = neighbourhood_group,
    neighborhood = neighbourhood) %>% 
  filter(borough != "Staten Island") %>% 
  select(price, stars, borough, neighborhood, room_type)

```

## Fit the first model

```{r}
fit = lm(price ~ stars + borough, data = nyc_airbnb)

fit

summary(fit)

fit %>% 
  broom::tidy() %>% 
  mutate(
    term = str_replace(term, "borough", "Borough: ")
  ) %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable(digits = 2)

```

## Let's change reference category.

```{r}
fit = 
  nyc_airbnb %>% 
  mutate(
    borough = fct_infreq(borough)
  ) %>% 
  lm(price ~ stars + borough, data = .)

fit %>% 
  broom::tidy() %>% 
  mutate(
    term = str_replace(term, "borough", "Borough: ")
  ) %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable(digits = 2)

fit %>% 
  broom::glance() %>% 
  select(AIC)

```

## Diagnostics - often done by getting residuals then looking at them
## Assumptions are: should be mean zero and constant varianc

In this example some of the assumptions aren't being met, but it's such a large sample size eventually everything is normally distributed anyway.

```{r}
modelr::add_residuals(nyc_airbnb, fit) %>% 
  ggplot(aes(x = stars, y = resid)) +
  geom_point()

nyc_airbnb %>% 
  modelr::add_residuals(fit) %>% 
  ggplot(aes(x = borough, y = resid)) +
  geom_violin() +
  ylim(-250, 250)
```

## Hypothesis testing

one coefficient (let's say `stars`).

```{r}
fit %>% 
  broom::tidy()

fit_null = lm(price ~ stars, data = nyc_airbnb)
fit_alt = lm(price ~ stars + borough, data = nyc_airbnb) 
# if you want to test these two against each other, an F test and get sums of squares 

# short hand:

anova(fit_null, fit_alt) %>% 
  broom::tidy()

# it's a small p-value you should probably put borough in your model

```


